\newpage
\begin{center}
    \section*{Acknowledgements}
\end{center}
I would like to give a special thanks to Mervyn White of the University of Bristol for his continued support throughout this project and the many hours we have spent discussing it. I would also like to acknowledge Simon Hughes for his continued support throughout the project as part of Everoze, the industrial partner for this project. Nicolas Chouler has been invaluable in his guidance on agrivoltaic expertise.  

\vspace{20mm}
\noindent DECLARATION
    \vspace{10mm}
    \begin{adjustwidth}{12mm}{12mm}
    
        \textit{The accompanying research project report entitled:  DEVELOPING A MATHEMATICAL MODEL FOR A HIGH DENSITY PUMPED HYDRO ENERGY STORAGE SYSTEM is submitted in the fourth year of study towards an application for the degree of ``Master of Engineering" in Engineering Design at the University of Bristol. The report is based on independent work by the candidate. All contributions from others have been acknowledged above. The views expressed within the report are those of the author and not of the University of Bristol.}
    
    \end{adjustwidth}

\vspace{20mm}
\noindent I hereby declare that the above statements are true.

\begin{center}
    \vfill%
    \begin{tabular}[t]{l}
        Signed (authors)\vspace{5mm}\\
        \rule{40em}{0.2pt}
    \end{tabular}%
    
    \vfill%
    \begin{tabular}[t]{l}
        Full Names \vspace{5mm}\\
        \rule{40em}{0.2pt}
    \end{tabular}%
    
    \vfill%
    \begin{tabular}[t]{l}
        Date \vspace{5mm}\\
        \rule{40em}{0.2pt}
    \end{tabular}%
    \vfill
\end{center}